\documentclass[a4paper,10pt]{article}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[ansinew]{inputenc}
\usepackage{bm}
\usepackage{float}
\usepackage{url}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphics}
\usepackage{subfigure}
\usepackage[numbers]{natbib}
\usepackage[small]{caption}
\usepackage{url}



\textwidth 7 in \oddsidemargin -0.2 in \setlength{\parindent}{0in}

\title{Instructions to Prepare Camera-ready Papers}
\author{}
\date{}

\begin{document}
\maketitle

For the camera-ready paper, please make sure that you follow the
next instructions

\begin{enumerate}
    \item Install the package \texttt{fancyhdr.sty}. The
    \texttt{aistats.sty} file will make use of it.
    \item Begin your document with
    \begin{flushleft}
    \texttt{\textbackslash documentclass[twoside]\{article\}}\\
    \texttt{\textbackslash usepackage[accepted]\{aistats2e\}}
    \end{flushleft}
    The \texttt{twoside} option for the class article allows the
    package \texttt{fancyhdr.sty} to include headings for even and
    odd numbered pages. The option \texttt{accepted} for the package
    \texttt{aistats.sty} will write a copyright notice at the end of
    the first column of the first page.
    \item After $\texttt{\textbackslash
    begin\{document\}}$, write
    \begin{flushleft}
    \texttt{\textbackslash begin\{document\}}\\
    \texttt{\textbackslash runningtitle\{Provide here the title of your
    paper\}}\\
    \texttt{\textbackslash runningauthor\{Provide here the surnames of the authors of your paper, all separated by
    commas\}}\\
    \texttt{\textbackslash checkheadings}
    \end{flushleft}
    The text that appears as argument in \texttt{\textbackslash runningtitle}
    will be printed as a heading in the \emph{even} pages. The text that appears as argument in \texttt{\textbackslash runningauthor}
    will be printed as a heading in the \emph{odd} pages.

    If the title of your paper is too long, \texttt{\textbackslash
    checkheadings} will print a warning message as heading title
    instead. The same will happen if there are too many authors
    appearing as argument in \texttt{\textbackslash
    runningauthor}.\\

    If a warning message is printed, please provide shorter versions
    of your paper's title and/or paper's authors, inside \texttt{\textbackslash runningtitle} and/or \texttt{\textbackslash
    runningauthor}.

    \item Use the sample2e.tex as an example.

    \item Please, don't change the layout given by the style file. If you have any
    question contact the publications chair.


\end{enumerate}


\end{document}
